Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-22 grove-paper.tex
Updates from Overleaf

Contrast this

@@

\begin{figure}
\centering
\begin{tikzpicture}
\path (0,0)       node {\includegraphics[scale=0.5]{graphviz/wrapping/1.dot}};
\path (0cm,-4cm)  node {\includegraphics[scale=0.5]{graphviz/wrapping/2.dot}};
\path (0cm,-8cm)  node {\includegraphics[scale=0.5]{graphviz/wrapping/3.dot}};
\path (0cm,-12cm) node {\includegraphics[scale=0.5]{graphviz/wrapping/4.dot}};
\path (0cm,-16cm) node {\includegraphics[scale=0.5]{graphviz/wrapping/5.dot}};
\end{tikzpicture}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

Before further exploring how to merge changes from multiple users,
we want to point out a common idiom

>>>>

@@

\begin{figure}
\centering
TODO: naive add that creates a conflict
\begin{tikzpicture}
\path (0,0)       node {\includegraphics[scale=0.5]{graphviz/wrapping/1.dot}};
\path (0cm,-4cm)  node {\includegraphics[scale=0.5]{graphviz/wrapping/2.dot}};
\path (0cm,-8cm)  node {\includegraphics[scale=0.5]{graphviz/wrapping/3.dot}};
\path (0cm,-12cm) node {\includegraphics[scale=0.5]{graphviz/wrapping/4.dot}};
\path (0cm,-16cm) node {\includegraphics[scale=0.5]{graphviz/wrapping/5.dot}};
\end{tikzpicture}
\caption{Wrapping}
\label{fig:Wrapping}
\end{figure}

Before further exploring how to merge changes from multiple users,
we want to point out a common idiom that we call \emph{wrapping}.
Consider the first graph in Figure~\ref{fig:Wrapping}, which
represents the code \texttt{$\lambda$ x . x}, and suppose
the user's cursor is in the body field of the lambda (i.e., around the variable
reference to \texttt{x} in the body of the lambda).

If the user requests that a plus be inserted,
the editor may notice that there is something already in that hole.
A naive editor could certainly add the plus by creating a new
edge from the body index of the lambda to a freshly created \texttt{plus} vertex.
This would result in a conflict between the \texttt{plus} and the existing \texttt{var}
as shown in Figure~REF:TODO.
A better user experience
would be interpret the request for a plus to mean to
take whatever (if anything) is in the cursor
and place it as a child of the plus.
This \emph{wraps} the existing \texttt{var} in the \texttt{plus}
and results in the code \texttt{$\lambda$ x . x + \hole}.
(This is similar to the behavior in other structure editors such as in CITE:TODO.)
Translating this into edge deletes and adds results in the sequence of graphs in Figure~\ref{fig:Wrapping}.
Note that this is a layer above
